Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 measurements.tex
Some changes in the measurements description and couple of in the abstract

For the plots in the mentioned figures from the encoder goodput measurements,
\ac{RLNC} presents the worst performance in terms of goodput and
\ac{TSNC} with $dep = 16$, the best regardless of the \ac{Raspi} model.
Given that the processing time depends in the amount of coded packets
required to create, \ac{RLNC} is the slowest to process since it must
use all of the $g$ original packets. Later, sparse codes process the data
at a larger rate since less packets are being mixed when creating a
coded packet. The caveat of these schemes is that the sparser the code,
the more probable the ocurrences of \ac{l.d.} packets is. So, basically
the sparser the codes, then more overhead due to transmissions of \ac{l.d.}
packets they have since it is more likely to generate the same set of
packets. Excluding the coding coefficients overhead, the overhead due to
transmissions of \ac{l.d.} packets can be very high.
For example, if we consider \ac{TSNC} with $dep=16$ and $g = 16$, the budget
in this case permits to send up to 32 packets which is $2\times$ the generation
size for an overhead of $100\%$ excluding the one from the coding
coefficients. This happens because \ac{TSNC} is allowed to add too much
redundancy in this case, which permits it to use a very low code density $d$.
For \ac{RLNC} this is not the case, since the occurrence of \ac{l.d.} coded
packets is low. Even for $GF(2)$, the average amount of redundancy has proven
to be 1.6 packets after $g$ have been transmitted.

%
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_encoder_Binary_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $q = 2$}}
        \label{fig:enc_good_rasp2_gen_gf2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_encoder_Binary8_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $q = 2^8$}}
        \label{fig:enc_good_rasp2_gen_gf256}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_encoder_Binary_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $q = 2,\ g=16$}}
        \label{fig:enc_good_rasp2_packet_gf2}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_encoder_Binary8_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $q = 2^8,\ g=16$}}
        \label{fig:enc_good_rasp2_packet_gf256}
    \end{subfigure}
    \caption[]
    {\small Encoder goodput measurements for the \ac{Raspi} 2}
    \label{fig:enc_good_rasp2}
\end{figure*}

>>>>

For the plots in the mentioned figures from the encoder goodput measurements,
\ac{RLNC} presents the worst performance in terms of goodput and
\ac{TSNC} with $dep = 16$, the best regardless of the \ac{Raspi} model.
Given that the processing time depends in the amount of coded packets
required to create, \ac{RLNC} is the slowest to process since it must
use all of the $g$ original packets. Later, sparse codes process the data
at a larger rate since less packets are being mixed when creating a
coded packet. The caveat of these schemes is that the sparser the code,
the more probable the ocurrences of \ac{l.d.} packets is. So, basically
the sparser the codes, then more overhead due to transmissions of \ac{l.d.}
packets they have since it is more likely to generate the same set of
packets. Excluding the coding coefficients overhead, the overhead due to
transmissions of \ac{l.d.} packets can be very high.
For example, if we consider \ac{TSNC} with $dep=16$ and $g = 16$, the budget
in this case permits to send up to 32 packets which is $2\times$ the generation
size for an overhead of $100\%$ excluding the one from the coding
coefficients. This happens because \ac{TSNC} is allowed to add too much
redundancy in this case, which permits it to use a very low code density $d$.
For \ac{RLNC} this is not the case, since the occurrence of \ac{l.d.} coded
packets is low. Even for $GF(2)$, the average amount of redundancy has proven
to be 1.6 packets after $g$ have been transmitted, much less than the
cases where sparse codes are employed. Overall, we observe that there is
a trade-off between goodput and \ac{l.d.} coded packets transmission
overhead.
%
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_encoder_Binary_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $q = 2$}}
        \label{fig:enc_good_rasp2_gen_gf2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_encoder_Binary8_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $q = 2^8$}}
        \label{fig:enc_good_rasp2_gen_gf256}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_encoder_Binary_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $q = 2,\ g=16$}}
        \label{fig:enc_good_rasp2_packet_gf2}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_encoder_Binary8_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $q = 2^8,\ g=16$}}
        \label{fig:enc_good_rasp2_packet_gf256}
    \end{subfigure}
    \caption[]
    {\small Encoder goodput measurements for the \ac{Raspi} 2}
    \label{fig:enc_good_rasp2}
\end{figure*}

### 2016-06-06 raspi_journal.tex
Some changes in the measurements description and couple of in the abstract

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{Deploying a large-scale and configurable testbed for
  networking and storage can be challenging, not only due to the
  inherent costs of the hardware, but due to maintenance challenges
  and ability to replicate results consistently. The latter requires
  not only the devices to run the same operating system (OS), but also
  have exactly the same configurations and software packages. This
  paper presents the design, step-by-step setup, and configuration of
  an inexpensive testbed using Raspberry Pi devices for networking
  (wireless or wired) and storage applications, although the
  architecture can be used for other applciations that require
  replicable results.  Specifically, we provide an in-depth
  performance evaluation for network coding, a new paradigm in
  networking and storage, and demonstrating the processing
  capabilities and energy behaviour of various code constructions and
  algorithms over different Raspberry Pi models. Our results show that
  processing speeds of more than 80 Mbps and 800 Mbps are attainable
  for a wide array of configurations are attainable for the Raspberry
  Pi Model 1 and 2, respectively, and that processing energy for
  network coding is below 1 nJ/bit in a large regime and even an order
  of magnitude lower for some algorithms.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}  
\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}
\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize\ttfamily,
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  %commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  %escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  escapeinside={<@}{@>}
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  %keywordstyle=\color{blue},       % keyword style
  %language=Bash,                 % the language of the code
  otherkeywords={*,...},           % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  %stringstyle=\color{mymauve},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
  title=\lstname,                  % show the filename of files included with \lstinputlisting; also try caption instead of title
  xleftmargin=5mm,
  xrightmargin=5mm,
  columns=flexible,
  upquote=true
}

>>>>

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{Deploying a large-scale and configurable testbed for
  networking and storage can be challenging, not only due to the
  inherent costs of the hardware, but due to maintenance challenges
  and ability to replicate results consistently. The latter requires
  not only the devices to run the same operating system (OS), but also
  have exactly the same configurations and software packages. This
  paper presents the design, step-by-step setup, and configuration of
  an inexpensive testbed using Raspberry Pi devices for networking
  (wireless or wired) and storage applications, although the
  architecture can be used for other applications that require
  replicable results.  Specifically, we provide an in-depth
  performance evaluation for network coding, a new paradigm in
  networking and storage, and demonstrating the processing
  capabilities and energy behaviour of various code constructions and
  algorithms over different Raspberry Pi models. Our results show that
  processing speeds of more than 80 Mbps and 800 Mbps are attainable
  for a wide array of configurations are attainable for the Raspberry
  Pi Model 1 and 2, respectively, and that processing energy per bit for
  network coding is below 1 nJ in a large regime and even an order
  of magnitude lower for some algorithms.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}
\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize\ttfamily,
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  %commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  %escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  escapeinside={<@}{@>},
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  %keywordstyle=\color{blue},       % keyword style
  %language=Bash,                 % the language of the code
  otherkeywords={*,...},           % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  %stringstyle=\color{mymauve},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
  title=\lstname,                  % show the filename of files included with \lstinputlisting; also try caption instead of title
  xleftmargin=5mm,
  xrightmargin=5mm,
  columns=flexible,
  upquote=true
}
